---
title: "615 Shiny"
output: html_document
author: Ziheng Li
date: "2024-11-15"
---


```{r}
#install.packages("shiny")
library(shiny)
```
```{r}
#library(shiny)
ui <- fluidPage(
  "Hello, world!"
)
server <- function(input, output, session) {
}
shinyApp(ui, server)

```


```{r}
#Hadley_1 
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)
server <- function(input, output, session) {
  output$summary <- renderPrint({
    dataset <- get(input$dataset, "package:datasets")
    summary(dataset)
  })
  
  output$table <- renderTable({
    dataset <- get(input$dataset, "package:datasets")
    dataset
  })
}
shinyApp(ui, server)
```

```{r}
#Hadley_2

ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)
server <- function(input, output, session) {
  # Create a reactive expression
  dataset <- reactive({
    get(input$dataset, "package:datasets")
  })

  output$summary <- renderPrint({
    # Use a reactive expression by calling it like a function
    summary(dataset())
  })
  
  output$table <- renderTable({
    dataset()
  })
}
shinyApp(ui, server)

```

The difference between the two is that we use a new mechanism: reaction expressions. Duplicating code is bad practice in any type of programming; it wastes computational resources and, more importantly, makes it harder to maintain or debug the code.

2.3.5 
#1
renderText(str(lm(mpg ~ wt, data = mtcars)))

#2
```{r}
ui <- fluidPage(

  plotOutput("plot", width = "700px", height = "300px")
)

server <- function(input, output, session) {
  output$plot <- renderPlot({

    set.seed(123)  
    random_numbers <- runif(5)
    

    plot(1:5, random_numbers, main = "Scatterplot of Random Numbers",
         xlab = "Index", ylab = "Random Value", pch = 19)
  }, res = 96)

  # Provide a textual description of what the plot shows
  output$plotDesc <- renderText({
    "This scatterplot displays five randomly generated numbers plotted against their respective indices from 1 to 5. Each point represents the value of a random number at that position."
  })
}

# Run the application
shinyApp(ui = ui, server = server)
```
#3
```{r}
library(DT)
ui <- fluidPage(
  DTOutput("table")  # Use DTOutput from the DT package
)

server <- function(input, output, session) {
  output$table <- renderDT({
    mtcars
  }, options = list(
    pageLength = 5,
    searching = FALSE,  
    ordering = FALSE,   
    lengthChange = FALSE,   
    info = FALSE,  
    paging = FALSE  
  ))
}


shinyApp(ui = ui, server = server)
```
#4
```{r}
#install.packages("reactable")
library(reactable)

reactable(iris)

library(shiny)
library(reactable)

ui <- fluidPage(
  reactableOutput("table")
)

server <- function(input, output) {
  output$table <- renderReactable({
    reactable(iris)
  })
}

shinyApp(ui, server)
```

3.3.6
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)
```

```{r}
server1 <- function(input, output, session) { 
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

server2 <- function(input, output, session) {
  output$greeting <- renderText({
    greeting <- paste0("Hello ", input$name)
    greeting
  })
}

server3 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

```

```{r}
#install.packages("DiagrammeR")
library(DiagrammeR)


graph1 <- grViz("
digraph server1 {
  graph [layout = dot]
  
  node [shape = circle]
  input_a [label = 'input$a']
  input_b [label = 'input$b']
  input_d [label = 'input$d']
  
  node [shape = box]
  c [label = 'c()']
  e [label = 'e()']
  
  node [shape = plaintext]
  output_f [label = 'output$f']
  
  input_a -> c
  input_b -> c
  c -> e
  input_d -> e
  e -> output_f
}
")

graph1

```
```{r}
graph2 <- grViz("
digraph server2 {
  graph [layout = dot]
  
  node [shape = circle]
  input_x1 [label = 'input$x1']
  input_x2 [label = 'input$x2']
  input_x3 [label = 'input$x3']
  input_y1 [label = 'input$y1']
  input_y2 [label = 'input$y2']
  
  node [shape = box]
  x [label = 'x()']
  y [label = 'y()']
  
  node [shape = plaintext]
  output_z [label = 'output$z']
  
  input_x1 -> x
  input_x2 -> x
  input_x3 -> x
  input_y1 -> y
  input_y2 -> y
  x -> output_z
  y -> output_z [label = '/', fontsize = 12]
}
")

graph2

```
```{r}
graph3 <- grViz("
digraph server3 {
  graph [layout = dot]
  
  node [shape = circle]
  input_a [label = 'input$a']
  input_b [label = 'input$b']
  input_c [label = 'input$c']
  input_d [label = 'input$d']
  
  node [shape = box]
  a [label = 'a()']
  b [label = 'b()']
  c [label = 'c()']
  d [label = 'd()']
  
  input_a -> a
  a -> b
  input_b -> b
  b -> c
  input_c -> c
  c -> d
  input_d -> d
}
")

graph3

```

#3.3.6 3
The reason the code may fail or cause confusion is due to the use of var and range as names for reactive expressions in Shiny, and using these names for reactive expressions can lead to name conflicts and unexpected behavior

#4.8
```{r}
ui <- fluidPage(
    numericInput("num1", "Enter number 1:", 1),
    numericInput("num2", "Enter number 2:", 1),
    textOutput("sum"),
    textOutput("product")
)

server <- function(input, output, session) {
    sum <- reactive({
        input$num1 + input$num2
    })
    
    product <- reactive({
        input$num1 * input$num2
    })
    
    output$sum <- renderText({
        paste("Sum:", sum())
    })
    
    output$product <- renderText({
        paste("Product:", product())
    })
}
shinyApp(ui, server)

```
```{r}
library(DiagrammeR)

grViz("
digraph shiny_app {
  graph [layout = dot]
  
  node [shape = circle]
  input_num1 [label = 'input$num1']
  input_num2 [label = 'input$num2']
  
  node [shape = box]
  sum [label = 'sum()']
  product [label = 'product()']
  
  node [shape = plaintext]
  output_sum [label = 'output$sum']
  output_product [label = 'output$product']
  
  input_num1 -> sum
  input_num2 -> sum
  input_num1 -> product
  input_num2 -> product
  sum -> output_sum
  product -> output_product
}
")
```

#4.8
```{r}
#library(shiny)
#library(dplyr)

ui <- fluidPage(
  titlePanel("Dynamic Row Number in Data Tables"),
  
  # Select input to choose number of rows to display
  selectInput("nRows", "Number of Rows:", 
              choices = c(5, 10, 15, 20, 25, 50, 100), selected = 10),
  
  # Table output
  DTOutput("dataTable")
)

server <- function(input, output) {
  # Render the data table
  output$dataTable <- renderDT({
    datatable(
      iris,  # Using the built-in iris dataset for demonstration
      options = list(pageLength = as.numeric(input$nRows))
    )
  })
}

shinyApp(ui = ui, server = server)

```

```{r}
ui <- fluidPage(
    titlePanel("Navigate Narratives"),
    actionButton("prev", "Previous", icon = icon("arrow-left")),
    actionButton("next", "Next", icon = icon("arrow-right")),
    textOutput("narrative")
)

server <- function(input, output, session) {
    narratives <- c(
        "Narrative One: The beginning of our journey.",
        "Narrative Two: The challenge emerges.",
        "Narrative Three: Overcoming obstacles.",
        "Narrative Four: The triumphant conclusion."
    )

    narrative_index <- reactiveVal(1)

    observeEvent(input$Next, {
        current_index <- narrative_index()
        if (current_index >= length(narratives)) {
            narrative_index(1)  # Wrap around to the first narrative
        } else {
            narrative_index(current_index + 1)
        }
    })

    observeEvent(input$prev, {
        current_index <- narrative_index()
        if (current_index <= 1) {
            narrative_index(length(narratives))  # Wrap to the last narrative
        } else {
            narrative_index(current_index - 1)
        }
    })

    output$narrative <- renderText({
        narratives[narrative_index()]
    })
}

shinyApp(ui = ui, server = server)

```

